Bringing the Power of eBPF to Open vSwitch

### 2018-10-29 paper.tex
Add XDP reference
Remove P4 related stuff
Add conclusion

>>>>

The eBPF project originally had the ambitious goal of replacing the fixed
kernel datapath with a dynamic datapath that may be injected on demand, while
keeping the design and operation essentially the same. This would solve
distribution and maintenance issues, as the version of the datapath would be
distributed with the OVS userspace package; furthermore, it would outline a
path to allow OVS to continue to process packets in the kernel without the use
of an OVS-specific kernel module, acheiving the goals of other recent
work~\cite{ovs_tc}. Collectively, this would allow the datapath logic to be
extended and modified more easily, while reducing the maintenance burden for
that code. Longer term, with a more flexible code base, many performance and
feature improvements could be made and more easily, as the constraints around
backwards compatibility of the fixed kernel ABI could be relaxed.

While the basic use cases for implementing the OpenFlow forwarding model can be
achieved in a straightforward manner in OVS-eBPF, implementing the full
capabilities of the current OVS datapath is more difficult within the bounds of
the BPF verification engine~\cite{extensible_ovs}. This paper explored an
additional approach which makes use of another datapath implementation that OVS
contains in userspace. Rather than building an extensible datapath and
inserting this logic into the kernel at runtime, the packets can be efficiently
directed to userspace for network processing using AF\_XDP sockets. The
userspace datapath implementation has none of the distribution, maintenance or
compatibility issues that the kernel implementation has, so at face value this
appears to serve many of the original goals of the OVS-eBPF project.

Over the course of exploring the use of AF\_XDP sockets, multiple design
choices were made with the goal of optimal performance in mind. Future
evaluation of this project should investigate the tradeoffs made with these
decisions, and how they affect the configuration and deployment of the
implementation. This implementation contains a lot of technical parallels with
the OVS-DPDK project, which puts certain constraints on deployment such as the
configuration of devices and the dedication of CPU and memory resources to the
datapath. In some deployment environments, these may not be feasible
constraints to place on OVS, and the existing kernel implementation does not
require such constraints.
